Tropical Andes Functional diversity for plants and Frugivores

### 2024-09-03 code/L2/L2_1_TropicalAndes_funcdiv.Rmd
comment out saving individual maps, add histograms, changing summarizing fdis value to mean instead of sum (fixing issue), and other minor fixes

spatial_fdis_frugivore_grid <- TAGrid_100km %>%
   st_join(spatial_fdis_frugivore) %>%
   group_by(cellid) %>%
   summarize(fdis_value = sum(fdis_frugivore, na.rm = TRUE)) %>%
   ungroup()
```

@@

```{r}
frugivoregridFDisTA_100km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_frugivore_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    ggtitle("100 km") +
    scale_fill_distiller(palette = "YlOrBr", direction = 1) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
frugivoregridFDisTA_100km
```

```{r}
ggsave("frugivoregridFDisTA_100km.png", frugivoregridFDisTA_100km, path = figure_path)
# Extract cell values
frugivore_cellFDis_100km <- spatial_fdis_frugivore_grid
hist(frugivore_cellFDis_100km$fdis_value)
```

@@

  spatial_fdis_frugivore_grid <- TAGrid %>%
   st_join(spatial_fdis_frugivore) %>%
   group_by(cellid) %>%
   summarize(fdis_value = sum(fdis_frugivore, na.rm = TRUE)) %>%
   ungroup()

  frugivoregridFDisTA <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_frugivore_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    scale_fill_distiller(palette = "YlOrBr", direction = 1) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
  frugivoregridFDisTA

@@

```{r}
# add title to maps
(frugivoregridFDisTA_75km <- frugivoregridFDisTA_75km +
    ggtitle("75 km")
)
ggsave("frugivoregridFDisTA_75km.png", frugivoregridFDisTA_75km, path = figure_path)
```

@@

```{r}
# add title to maps
(frugivoregridFDisTA_50km <- frugivoregridFDisTA_50km +
    ggtitle("50 km")
)
ggsave("frugivoregridFDisTA_50km.png", frugivoregridFDisTA_50km, path = figure_path)
```

@@

```{r}
# add title to maps
(frugivoregridFDisTA_25km <- frugivoregridFDisTA_25km +
    ggtitle("25 km")
)
ggsave("frugivoregridFDisTA_25km.png", frugivoregridFDisTA_25km, path = figure_path)
```

@@

```{r}
# add title to maps
(frugivoregridFDisTA_10km <- frugivoregridFDisTA_10km +
    ggtitle("10 km")
)
ggsave("frugivoregridFDisTA_10km.png", frugivoregridFDisTA_10km, path = figure_path)
```

```{r}
# Generate coordinates
subset_coords_frugivore_5km <-site_loc_key_frugivore_5km[rowSums(PAM_frugivore_site_final_5km) >= 4, ]
subset_coords_frugivore_sp_5km <-subset_coords_frugivore_5km[,1:2 ]

@@

  # Group by cellid and summarize fdis values
  summarized <- joined %>%
    group_by(cellid) %>%
    summarize(fdis_value = sum(fdis, na.rm = TRUE)) %>%
    ungroup()

@@

```{r}
frugivoregridFDisTA_5km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_frugivore_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    scale_fill_distiller(palette = "YlOrBr", direction = 1) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
  frugivoregridFDisTA_5km
frugivore_cellFDis_5km <- spatial_fdis_frugivore_grid
```

```{r}
# add title to maps
(frugivoregridFDisTA_5km <- frugivoregridFDisTA_5km +
    ggtitle("5 km")
)
ggsave("frugivoregridFDisTA_5km.png", frugivoregridFDisTA_5km, path = figure_path)
```

@@

spatial_fdis_plant_grid <- TAGrid_100km %>%
   st_join(spatial_fdis_plant) %>%
   group_by(cellid) %>%
   summarize(fdis_value = sum(fdis_plant, na.rm = TRUE)) %>%
   ungroup()
```

@@

```{r}
plantgridFDisTA_100km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_plant_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    ggtitle("100 km") +
    scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0,7.5)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
plantgridFDisTA_100km
```

```{r}
ggsave("plantgridFDisTA_100km.png", plantgridFDisTA_100km, path = figure_path)
# Extract cell values
plant_cellFDis_100km <- spatial_fdis_plant_grid
hist(plant_cellFDis_100km$fdis_value)
```

@@

  # Use three fewer cores than available
  num_cores <- detectCores() - 3
  cl <- makeCluster(num_cores)
  registerDoParallel(cl)

  on.exit(stopCluster(cl)) # Ensure the cluster is stopped when the function exits

  tryCatch({
    # Generate the grid
    TAGrid <- TApoly %>%
      st_make_grid(cellsize = resolution_meters) %>%
      st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
      st_cast("MULTIPOLYGON") %>%
      st_sf() %>%
      mutate(cellid = row_number())

    # Check if TAGrid is empty
    if (nrow(TAGrid) == 0) {
      stop("Error: No valid grid cells after intersection.")
    }

    # Divide the indices of the grid into chunks for parallel processing
    chunk_indices <- split(seq_len(nrow(TAGrid)), rep(1:num_cores, each = ceiling(nrow(TAGrid) / num_cores), length.out = nrow(TAGrid)))

    # Process chunks in parallel
    results_list <- foreach(indices = chunk_indices, .combine = rbind, .packages = c("sf", "dplyr")) %dopar% {
      chunk <- TAGrid[indices, ]

      # Perform the intersection
      intersected <- st_intersection(spatial_fdis_plant, chunk)

      # Calculate cellid for intersected
      intersected$cellid <- st_intersects(intersected, chunk)$nn

      # Ensure that intersected is a data frame
      as.data.frame(intersected)
    }

    # Combine all chunk results into a single data frame
    spatial_fdis_plant <- do.call(rbind, results_list)

    # Ensure the combined result is a data frame
    spatial_fdis_plant <- as.data.frame(spatial_fdis_plant)

    # Debugging: Check if 'cellid' column exists
    if (!"cellid" %in% colnames(spatial_fdis_plant)) {
      stop("Error: 'cellid' column not found in spatial_fdis_plant.")
    }

    # Summarize fdis values per grid cell
    spatial_fdis_plant_grid <- spatial_fdis_plant %>%
      group_by(cellid) %>%
      summarize(fdis_value = sum(fdis_plant, na.rm = TRUE)) %>%
      right_join(as.data.frame(TAGrid), by = "cellid")

    # Convert the grid to sf
    spatial_fdis_plant_grid <- st_as_sf(spatial_fdis_plant_grid)

    # Create the plot
    plantgridFDisTA <- ggplot() +
      geom_sf(data = Americas, fill = "white") +
      geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
      geom_sf(data = spatial_fdis_plant_grid, aes(fill = fdis_value), color = NA) +
      labs(fill = "FDis") +
      scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0, 7.5)) +
      coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
      theme(panel.background = element_rect(fill = "lightblue"),
            text = element_text(size = 12),
            plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(angle = 45, hjust = 1))

    list(plantgridFDisTA = plantgridFDisTA, spatial_fdis_plant_grid = spatial_fdis_plant_grid)
  }, error = function(e) {
    message("Error in parallel processing: ", conditionMessage(e))
    NULL
  })
}
```

@@

```{r}
# add title to maps
(plantgridFDisTA_75km <- plantgridFDisTA_75km +
    ggtitle("75 km")
)
ggsave("plantgridFDisTA_75km.png", plantgridFDisTA_75km, path = figure_path)
```

@@

```{r}
# add title to maps
(plantgridFDisTA_50km <- plantgridFDisTA_50km +
    ggtitle("50 km")
)
ggsave("plantgridFDisTA_50km.png", plantgridFDisTA_50km, path = figure_path)
```

@@

```{r}
# add title to maps
(plantgridFDisTA_25km <- plantgridFDisTA_25km +
    ggtitle("25 km")
)
ggsave("plantgridFDisTA_25km.png", plantgridFDisTA_25km, path = figure_path)
```

@@

```{r}
# add title to maps
(plantgridFDisTA_10km <- plantgridFDisTA_10km +
    ggtitle("10 km")
)
ggsave("plantgridFDisTA_10km.png", plantgridFDisTA_10km, path = figure_path)
```

```{r}
# Generate coordinates
subset_coords_plant_5km <-site_loc_key_plant_5km[rowSums(PAM_plant_site_final_5km) >= 4, ]
subset_coords_plant_sp_5km <-subset_coords_plant_5km[,1:2 ]

@@

@@

  # Perform spatial join
  joined <- st_join(grid_chunk, spatial_fdis_plant)

  # Group by cellid and summarize fdis values
  summarized <- joined %>%
    group_by(cellid) %>%
    summarize(fdis_value = sum(fdis_plant, na.rm = TRUE)) %>%
    ungroup()

@@

@@

# Convert to sf object if applicable
if ("geometry" %in% colnames(flattened_results)) {
  spatial_fdis_plant_grid <- st_as_sf(flattened_results)
} else {
  spatial_fdis_plant_grid <- flattened_results
}

# Check the structure of the final output
str(spatial_fdis_plant_grid)

@@

```{r}
plantgridFDisTA_5km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_plant_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    ggtitle("5 km") +
    scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0,6.5)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
plantgridFDisTA_5km
```

```{r}
plant_cellFDis_5km <- spatial_fdis_plant_grid
```

```{r}
# add title to maps
(plantgridFDisTA_5km <- plantgridFDisTA_5km +
    ggtitle("5 km")
)
ggsave("plantgridFDisTA_5km.png", plantgridFDisTA_5km, path = figure_path)
```

# Multi panel plots of FD maps
## Make sure all plots for the same taxa have the same legend scale
```{r}
plant_plot_legend <- function(plot){
  plot + scale_fill_distiller(palette = "Greens", direction = 1,limits = c(0, 6.5),
                              oob = scales::squish, breaks = seq(0, 6.5, by = 1)) +
    theme(legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10)) +
      annotation_scale(location = "bl", width_hint = 0.5)
}
frugivore_plot_legend <- function(plot){
  plot + scale_fill_distiller(palette = "YlOrBr", direction = 1,limits = c(0, 8.5),
                              oob = scales::squish, breaks = seq(0, 8.5, by = 1)) +
    theme(legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10)) +
      annotation_scale(location = "bl", width_hint = 0.5)
}
```

>>>>

spatial_fdis_frugivore_grid <- TAGrid_100km %>%
   st_join(spatial_fdis_frugivore, join = st_contains) %>%
   group_by(cellid) %>%
   summarize(fdis_value = mean(fdis_frugivore, na.rm = TRUE)) %>%
   ungroup()
```

@@

```{r}
frugivoregridFDisTA_100km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_frugivore_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    ggtitle("100 km") +
    scale_fill_distiller(palette = "YlOrBr", direction = 1, limits = c(0,0.8)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
frugivoregridFDisTA_100km
```

```{r}
#ggsave("frugivoregridFDisTA_100km.png", frugivoregridFDisTA_100km, path = figure_path)
# Extract cell values
frugivore_cellFDis_100km <- spatial_fdis_frugivore_grid
hist(frugivore_cellFDis_100km$fdis_value)
```

@@

  spatial_fdis_frugivore_grid <- TAGrid %>%
   st_join(spatial_fdis_frugivore) %>%
   group_by(cellid) %>%
   summarize(fdis_value = mean(fdis_frugivore, na.rm = TRUE)) %>%
   ungroup()

  frugivoregridFDisTA <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey") +
    geom_sf(data = spatial_fdis_frugivore_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    scale_fill_distiller(palette = "YlOrBr", direction = 1, limits = c(0,0.8)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
  frugivoregridFDisTA

@@

```{r}
# add title to maps
(frugivoregridFDisTA_75km <- frugivoregridFDisTA_75km +
    ggtitle("75 km")
)
#ggsave("frugivoregridFDisTA_75km.png", frugivoregridFDisTA_75km, path = figure_path)
```

@@

```{r}
# add title to maps
(frugivoregridFDisTA_50km <- frugivoregridFDisTA_50km +
    ggtitle("50 km")
)
#ggsave("frugivoregridFDisTA_50km.png", frugivoregridFDisTA_50km, path = figure_path)
```

@@

```{r}
# add title to maps
(frugivoregridFDisTA_25km <- frugivoregridFDisTA_25km +
    ggtitle("25 km")
)
#ggsave("frugivoregridFDisTA_25km.png", frugivoregridFDisTA_25km, path = figure_path)
```

@@

```{r}
# add title to maps
(frugivoregridFDisTA_10km <- frugivoregridFDisTA_10km +
    ggtitle("10 km")
)
#ggsave("frugivoregridFDisTA_10km.png", frugivoregridFDisTA_10km, path = figure_path)
```

```{r}
hist(frugivore_cellFDis_75km$fdis_value)
hist(frugivore_cellFDis_50km$fdis_value)
hist(frugivore_cellFDis_25km$fdis_value)
hist(frugivore_cellFDis_10km$fdis_value)
```

## 5 km
```{r}
# Generate coordinates
subset_coords_frugivore_5km <-site_loc_key_frugivore_5km[rowSums(PAM_frugivore_site_final_5km) >= 4, ]
subset_coords_frugivore_sp_5km <-subset_coords_frugivore_5km[,1:2 ]

@@

  # Group by cellid and summarize fdis values
  summarized <- joined %>%
    group_by(cellid) %>%
    summarize(fdis_value = mean(fdis, na.rm = TRUE)) %>%
    ungroup()

@@

```{r}
frugivoregridFDisTA_5km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey") +
    geom_sf(data = spatial_fdis_frugivore_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    scale_fill_distiller(palette = "YlOrBr", direction = 1, limits = c(0,0.8)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
frugivore_cellFDis_5km <- spatial_fdis_frugivore_grid
```

```{r}
# add title to maps
(frugivoregridFDisTA_5km <- frugivoregridFDisTA_5km +
    ggtitle("5 km")
)
#ggsave("frugivoregridFDisTA_5km.png", frugivoregridFDisTA_5km, path = figure_path)
hist(frugivore_cellFDis_5km$fdis_value)
```

@@

spatial_fdis_plant_grid <- TAGrid_100km %>%
   st_join(spatial_fdis_plant) %>%
   group_by(cellid) %>%
   summarize(fdis_value = mean(fdis_plant, na.rm = TRUE)) %>%
   ungroup()
```

@@

```{r}
plantgridFDisTA_100km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = spatial_fdis_plant_grid, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    ggtitle("100 km") +
    scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0,0.8)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
plantgridFDisTA_100km
```

```{r}
#ggsave("plantgridFDisTA_100km.png", plantgridFDisTA_100km, path = figure_path)
# Extract cell values
plant_cellFDis_100km <- spatial_fdis_plant_grid
hist(plant_cellFDis_100km$fdis_value)
```

@@

  # Generate the grid
  TAGrid <- TApoly %>%
    st_make_grid(cellsize = resolution_meters) %>%
    st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
    st_cast("MULTIPOLYGON") %>%
    st_sf() %>%
    mutate(cellid = row_number())

  spatial_fdis_plant$cellid <- st_intersects(spatial_fdis_plant, TAGrid)$nn

  spatial_fdis_plant_grid <- TAGrid %>%
   st_join(spatial_fdis_plant) %>%
   group_by(cellid) %>%
   summarize(fdis_value = mean(fdis_plant, na.rm = TRUE)) %>%
   ungroup()

    # Create the plot
    plantgridFDisTA <- ggplot() +
      geom_sf(data = Americas, fill = "white") +
      geom_sf(data = TApoly, fill = "lightgrey") +
      geom_sf(data = spatial_fdis_plant_grid, aes(fill = fdis_value), color = NA) +
      labs(fill = "FDis") +
      scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0,0.8)) +
      coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
      theme(panel.background = element_rect(fill = "lightblue"),
            text = element_text(size = 12),
            plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(angle = 45, hjust = 1))

    list(plantgridFDisTA = plantgridFDisTA, spatial_fdis_plant_grid = spatial_fdis_plant_grid)
  }
```

@@

```{r}
# add title to maps
(plantgridFDisTA_75km <- plantgridFDisTA_75km +
    ggtitle("75 km")
)
#ggsave("plantgridFDisTA_75km.png", plantgridFDisTA_75km, path = figure_path)
```

@@

```{r}
# add title to maps
(plantgridFDisTA_50km <- plantgridFDisTA_50km +
    ggtitle("50 km")
)
#ggsave("plantgridFDisTA_50km.png", plantgridFDisTA_50km, path = figure_path)
```

@@

```{r}
# add title to maps
(plantgridFDisTA_25km <- plantgridFDisTA_25km +
    ggtitle("25 km")
)
#ggsave("plantgridFDisTA_25km.png", plantgridFDisTA_25km, path = figure_path)
```

@@

```{r}
# add title to maps
(plantgridFDisTA_10km <- plantgridFDisTA_10km +
    ggtitle("10 km")
)
#ggsave("plantgridFDisTA_10km.png", plantgridFDisTA_10km, path = figure_path)
```

```{r}
hist(plant_cellFDis_75km$fdis_value)
hist(plant_cellFDis_50km$fdis_value)
hist(plant_cellFDis_25km$fdis_value)
hist(plant_cellFDis_10km$fdis_value)
```

## 5 km 
```{r}
# Generate coordinates
subset_coords_plant_5km <-site_loc_key_plant_5km[rowSums(PAM_plant_site_final_5km) >= 4, ]
subset_coords_plant_sp_5km <-subset_coords_plant_5km[,1:2 ]

@@

```{r}
# Determine number of cores to use
num_cores <- detectCores() - 3

@@

  # Perform spatial join
  joined <- st_join(grid_chunk, spatial_fdis_plant_5km)

  # Group by cellid and summarize fdis values
  summarized <- joined %>%
    group_by(cellid) %>%
    summarize(fdis_value = mean(fdis, na.rm = TRUE)) %>%
    ungroup()

@@

  list(as.data.frame(summarized_df))
}

@@

# Convert to sf object if applicable
if ("geometry" %in% colnames(flattened_results)) {
  spatial_fdis_plant_grid_5km <- st_as_sf(flattened_results)
} else {
  spatial_fdis_plant_grid_5km <- flattened_results
}

# Check the structure of the final output
str(spatial_fdis_plant_grid_5km)

@@

```{r}
plantgridFDisTA_5km <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey") +
    geom_sf(data = spatial_fdis_plant_grid_5km, aes(fill = fdis_value), color = NA) +
    labs(fill = "FDis") +
    scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0,0.8)) +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue"),
        text = element_text(size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))

plant_cellFDis_5km <- spatial_fdis_plant_grid_5km
```

```{r}
# add title to maps
(plantgridFDisTA_5km <- plantgridFDisTA_5km +
    ggtitle("5 km")
)
#ggsave("plantgridFDisTA_5km.png", plantgridFDisTA_5km, path = figure_path)
```

```{r}
hist(plant_cellFDis_5km$fdis_value)
```

# Multi panel plots of FD maps
## Make sure all plots for the same taxa have the same legend scale
```{r}
plant_plot_legend <- function(plot){
  plot + scale_fill_distiller(palette = "Greens", direction = 1, limits = c(0,0.8),
                              oob = scales::squish, breaks = seq(0, 0.8, by = 0.2)) +
    theme(legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10)) +
      annotation_scale(location = "bl", width_hint = 0.5)
}
frugivore_plot_legend <- function(plot){
  plot + scale_fill_distiller(palette = "YlOrBr", direction = 1, limits = c(0,0.8),
                              oob = scales::squish, breaks = seq(0, 0.8, by = 0.2)) +
    theme(legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10)) +
      annotation_scale(location = "bl", width_hint = 0.5)
}
```
